---
title: "Milestone 3"
author: "Heather VT., Kera Y., Marcelle C., Wilson D."
date: "April 13th, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "Milestone3/images_report/")
library(tidyverse)
library(gridExtra)
```



## Introduction

The current analysis seeks to explore the relationship between `self-rated sustainability importance` and `recycling frequency`. Additionally, the analysis also aims to determine whether this relationship is confounded by an `individual’s age` and `background (environmentally-conscious family)`, and analyze if a video about recycling changes individuals’ opinions on the importance of sustainability. With this purpose, we published a [survey](https://ubc.ca1.qualtrics.com/jfe/form/SV_4SJCJH59wUakrEF) using [UBC-hosted version of Qualtrics](https://ubc.ca1.qualtrics.com/) to collect responses to be used in this analysis.

## Methods

### Survey study design 

### Data collection methods

> Online survey with Qualtrics UBC
>
> Wanted to 

### Analysis methods

## Results

```{r load data, warning=FALSE}
# load data
tidy_data <- read.csv("../data/tidy_data.csv")

# factor relevel
tidy_data$recycling_freq <- tidy_data$recycling_freq %>% fct_relevel("Rarely","Sometimes","Usually","Always")
tidy_data$background <- tidy_data$background %>% fct_relevel("Yes","No")
tidy_data$watch <- tidy_data$watch %>% fct_relevel("Have watched","Will pass")
```


```{r summary table}
# Creating summary table
summary(tidy_data)
```

```{r}
head(tidy_data)
```

```{r ANOVA to find confounders}
#simple_model = lm(data=tidy_data, recycling_freq ~ self_rating_before)
#age_confounder = lm(data=tidy_data, recycling_freq ~ self_rating_before + age)
#background_confounder = lm(data=tidy_data, recycling_freq ~ self_rating_before + background)
#interaction_effects = lm(data=tidy_data, recycling_freq ~ self_rating_before + background*age)

#summary(simple_model)
```
## Discussion 

### Discussion of results

### Discussion of survey/study design



### NOTES for reference
 >3-5 page report

    > Your target audience is other Data Scientists who are not familiar with your project.
    Clearly introduce the survey topic and question you were interested in answering.
    Link to your study's data and code in the methods section of your report.
    Include effective visualizations and/or tables that help communicate your findings.
    Your discussion should have 2 key focuses:
        Discussing the results and findings of your survey and analysis of the survey data.
        Discussing your survey/study design, specifically:
        what did you do well to make this study as causal as possible?
        what was not done well and how did that effect your studies conclusions?
        what would you do differently next time to improve your survey/study design and why?
