---
title: "Milestone 3"
author: "Heather VT., Kera Y., Marcelle C., Wilson D."
date: "April 13th, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "Milestone3/images_report/")
library(tidyverse)
library(gridExtra)
```



## Introduction

The current analysis seeks to explore the relationship between `self-rated sustainability importance` and `recycling frequency`. Additionally, the analysis also aims to determine whether this relationship is confounded by an `individual’s age` and `background (environmentally-conscious family)`, and analyze if a video about recycling changes individuals’ opinions on the importance of sustainability. With this purpose, we published a [survey](https://ubc.ca1.qualtrics.com/jfe/form/SV_4SJCJH59wUakrEF) using [UBC-hosted version of Qualtrics](https://ubc.ca1.qualtrics.com/) to collect responses to be used in this analysis.

## Methods

### Survey study design 

### Data collection methods

> Online survey with Qualtrics UBC
>
> Wanted to 

### Analysis methods

## Results

```{r load data, warning=FALSE}
# load data
tidy_data <- read.csv("../data/tidy_data.csv")

# factor relevel
tidy_data$recycling_freq <- tidy_data$recycling_freq %>% fct_relevel("Rarely","Sometimes","Usually","Always")
tidy_data$background <- tidy_data$background %>% fct_relevel("Yes","No")
tidy_data$watch <- tidy_data$watch %>% fct_relevel("Have watched","Will pass")
```


```{r summary table}
# Creating summary table
summary(tidy_data)
```

```{r make not a factor}
# Changing recycling_freq to not be a factor for linear regression analysis.
tidy_data <- tidy_data %>%
  mutate(recycling_freq_nf = if_else(recycling_freq =="Always", 
                                     5, if_else(recycling_freq == "Usually",
                                     4, if_else(recycling_freq == "Sometimes",
                                     3, if_else(recycling_freq == "Rarely",
                                     2, if_else(recycling_freq == "Never",
                                     1, 0)))))) 



head(tidy_data)
```

```{r ANOVA to find confounders}
simple_model= lm(data=tidy_data, recycling_freq_nf ~ self_rating_before)
age_confounder= lm(data=tidy_data, recycling_freq_nf ~ self_rating_before + age)
background_confounder= lm(data=tidy_data, recycling_freq_nf ~ self_rating_before + background)
interaction_effects = lm(data=tidy_data, recycling_freq_nf ~ self_rating_before + background*age)

summary(simple_model)
```
> The simple model with just X and Y has a significant F-statistic, meaning we can reject the null hypothesis that there is no effect of X on Y.

> In order to understand if there are confounding variable though, we need to take a closer look and compare the simple linear model with the linear models that include confounding variables.

```{R test age confounder}
anova(simple_model, age_confounder)
```
> Age does not seem to be a significant factor in predicting recycling frequency. p-value>0.05

```{R background  confouners}
#summary(background_confounder)
anova(simple_model, background_confounder)
```
> Background does not seem to be a significant factor in predicting recycling frequency.

```{R interaction fx?}
summary(interaction_effects)

```
> There are no interaction effects, so we can just look at the single variables as potential confounders... (better explanation needed)


```{R all variables}
all_variables= lm(data=tidy_data, recycling_freq_nf ~ self_rating_before + background + age)

summary(all_variables)
```
> Including all predictive variables in the model shows that on average, for each unit increase in X, there is a 0.176 increase in y. This means that for every increase in self-importance of sustainability rating there is a 0.17 increase in frequency of recycling. The p-value is 0.000103, which is significant with an alpha of 0.05. Therefore, we can reject the null hypothesis and say that there is a positive relationship between self-rated importance of being sustianable and one's frequency of recycling.

#### Important assumptions:

- 1) There are only two possible confounding variables: age, background. In the literature it appears that income is a significant predictor of recycling frequency, which we did not include in our survey. (Schultz et al. 1995)
- 2) The strength of the (X,Y) association within each strata defined by the confounders is the same.
- 3) There is a simple linear relationshing in how Y varies accross the strata.

## Discussion 

### Discussion of results

### Discussion of survey/study design


### References
1) Schultz, P. W., Oskamp, S., & Mainieri, T. (1995). Who recycles and when? A review of personal and situational factors. Journal of Environmental Psychology, 15(2), 105-121. http://dx.doi.org/10.1016/0272-4944(95)90019-5.


### NOTES for reference
 >3-5 page report

    > Your target audience is other Data Scientists who are not familiar with your project.
    Clearly introduce the survey topic and question you were interested in answering.
    Link to your study's data and code in the methods section of your report.
    Include effective visualizations and/or tables that help communicate your findings.
    Your discussion should have 2 key focuses:
        Discussing the results and findings of your survey and analysis of the survey data.
        Discussing your survey/study design, specifically:
        what did you do well to make this study as causal as possible?
        what was not done well and how did that effect your studies conclusions?
        what would you do differently next time to improve your survey/study design and why?
