---
title: "Milestone2_EDA"
author: "Wilson D., Marcelle C."
date: "4/5/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

This dataset is aimed to answer the question "Does a person’s frequency of recycling influence her/his opinion and attitudes towards the importance of sustainability?". The description of columns as follows:

  - `Q1_1`: How important is being environmentally sustainable to you on a scale from 1-10?
  - `Q2`: How often do you generally recycle?
  - `Q3`: What is your age group?
  - `Q4`: Did you grow up in an environmentally-conscious family?
  - `Q5`: Will you watch the video? 
  - `Q6_1`: After watching this video about recycling, how important is sustainability to you on a self-ranked scale from 1-10 scale?

# Load Data

```{r load data, warning=FALSE}
#tidy data and give correct data type
tidy_data <- read_csv("../data/Sustainable Survey_April 4, 2019_18.11.csv", col_types = cols(.default = col_character()))[3:62,18:23]
tidy_data <- tidy_data %>% 
  mutate(Q1_1 = as.numeric(Q1_1),
         Q2 = as.factor(Q2),
         Q3 = as.factor(Q3),
         Q4 = as.factor(Q4),
         Q5 = as.factor(Q5),
         Q6_1 = as.numeric(Q6_1))

# factor relevel
tidy_data$Q2 <- tidy_data$Q2 %>% fct_relevel("Rarely","Sometimes","Usually","Always")
tidy_data$Q4 <- tidy_data$Q4 %>% fct_relevel("Yes","No")
tidy_data$Q5 <- tidy_data$Q5 %>% fct_relevel("Have watched","Will pass")
```


```{r summary table}
# Creating summary table
summary(tidy_data)
```

> Analyzing the summary table, we noticed:
>
> **Q1_1: How important is being environmentally sustainable to you on a scale from 1-10?**: 
>
> **Q2: How often do you generally recycle?**:
>
> **Q3: What is your age group?**: 60% of the participants are from the younger groups, having 20-29 years old. We had a considerable amount of people with 40+, but only 5% of the respondents are 35-39 years old.
>
> **Q4: Did you grow up in an environmentally-conscious family?**: 46.7% of the respondents grow up in an environmentally-conscious family.
>
> **Q5: Will you watch the video?**: Only 63% of the respondents confirmed that they watched the video.
>
> **Q6_1: After watching this video about recycling, how important is sustainability to you on a self-ranked scale from 1-10 scale?**: The self rank about sustainability importance after watching the video had a slightly higher mean and median than the first one (9 and 8.1 vs. 8 and 7.8, respectively). However, some people who didn't watch the video answered the last question, since we had 15 respondents who said on Q5 that they passed the video, and only 9 participants answered NA to Q6_1.

# EDA

```{r plot family vs. frequency}
tidy_data %>% 
  ggplot() +
  geom_bar(aes(x = Q2, fill = Q4)) +
  facet_grid(~Q4) +
  theme_bw() +
  labs(x = "How often do you recycle? ",
       title = "Frequency of recycling vs. Did you grow up in an environmentally-conscious family?") +
  scale_fill_discrete(name = "environmentally-conscious family?") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


> As we can see from the above plot, most of our respondent have a good recycling habit whether or not they live in a environmentally-consicous family. However, if one respondent did not grow up in an environmentally-conscious family then he/she may do not recycle at all.

```{r plot age group vs. sustainability importance before watching the video}
qplot(tidy_data$Q3, tidy_data$Q1_1, geom="boxplot") +
  ylim(0, 10) +
  theme_bw() +
  labs(x = "Age Group",
       y = "Sustainability Importance") +
  ggtitle("Sustainability Importance vs. Age Group") +
  theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5)) +
  theme(axis.text = element_text(size = 14),
       axis.title = element_text(size = 13))
```


> Analyzing the boxplots above is easy to see that older people (`35-39` and `40+` groups) consider sustainability more important than younger groups, having a higher mean (~9 in a scale from 1-10) and narrower range. Additionaly, the other 3 groups (`20-24`, `25-29` and `30-34`) have one outlier each, where at least one respondent of each of these groups evaluated sustainability with a considerable lower importance in comparison with the other participants from their respective group. However, it's important to take into account that we have fewer responses from the second oldest age group, which can distort the analysis.
