---
title: "Milestone2_EDA"
author: "Wilson D"
date: "4/5/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

This dataset is aimed to answer the question "Does a person’s frequency of recycling influence her/his opinion and attitudes towards the importance of sustainability?". The description of columns as follows:

  - `Q1_1`: How important is being environmentally sustainable to you on a scale from 1-10?
  - `Q2`: How often do you generally recycle?
  - `Q3`: What is your age group?
  - `Q4`: Did you grow up in an environmentally-conscious family?
  - `Q5`: Will you watch the video? 
  - `Q6_1`: After watching this video about recycling, how important is sustainability to you on a self-ranked scale from 1-10 scale?

# Load Data

```{r load data, warning=FALSE}
#tidy data and give correct data type
tidy_data <- read_csv("../data/Sustainable Survey_April 4, 2019_18.11.csv", col_types = cols(.default = col_character()))[3:62,18:23]
tidy_data <- tidy_data %>% 
  mutate(Q1_1 = as.numeric(Q1_1),
         Q2 = as.factor(Q2),
         Q3 = as.factor(Q3),
         Q4 = as.factor(Q4),
         Q5 = as.factor(Q5),
         Q6_1 = as.numeric(Q6_1))

# factor relevel
tidy_data$Q2 <- tidy_data$Q2 %>% fct_relevel("Rarely","Sometimes","Usually","Always")
tidy_data$Q4 <- tidy_data$Q4 %>% fct_relevel("Yes","No")
tidy_data$Q5 <- tidy_data$Q5 %>% fct_relevel("Have watched","Will pass")
```


```{r summary table}
# Creating summary table
summary(tidy_data)
```

> ***Need to be done*** Briefly discuss about the summary table.

# EDA

```{r plot family vs. frequency}
tidy_data %>% 
  ggplot() +
  geom_bar(aes(x = Q2, fill = Q4)) +
  facet_grid(~Q4) +
  theme_bw() +
  labs(x = "How often do you recycle? ",
       title = "Frequency of recycling vs. Did you grow up in an environmentally-conscious family?") +
  scale_fill_discrete(name = "environmentally-conscious family?") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


> As we can see from the above plot, most of our respondent have a good recycling habit whether or not they live in a environmentally-consicous family. However, if one respondent did not grow up in an environmentally-conscious family then he/she may do not recycle at all.
